# Support Vector Machine: a kernel machine

## The most popular kernel functions are 
1. the linear kernel: text classification, why?
  (1) Text is often linearly separable
  (2) Text has a lot of features
  (3) Linear kernel is faster:  LibLinear(library)
  (4) Less parameters to optimize: only need to optimize the C    regularization parameter

2. the polynomial kernel
3. the RBF (Gaussian) kernel
4. the string kernel

sc: http://www.svm-tutorial.com/2014/10/svm-linear-kernel-good-text-classification/

# Practice 

```{r}
library("RTextTools");
library("tm")
data <- read.csv('C:/temp/sunnyData.csv', header = TRUE)
data
```


```{r}
# Create the document term matrix
dtMatrix <- create_matrix(data["Text"])
dtMatrix
```

sparse/sparsity(稀疏):decide whether we should use a linear kernel.

```{r}
# Configure the training data
container <- create_container(dtMatrix, data$IsSunny, trainSize=1:11, virgin=FALSE)
container
 
# train a SVM Model
model <- train_model(container, "SVM", kernel="linear", cost=1)
model
```

create_container and train_model  methods are RTextTools methods.

the virgin=FALSE argument is here to tell RTextTools not to save an analytics_virgin-class object inside the container. This parameter does not interest us now but is required by the function.

```{r}
# new data
predictionData <- list("sunny sunny sunny rainy rainy", "rainy sunny rainy rainy", "hello", "", "this is another rainy world")
predictionData

#trace("create_matrix",edit=T)
# In the source code box that pops up, line 42 will have a misspelling of the word "acronym". Change the "A" to an "a" and hit "Save" - it should work fine after that.

# create a prediction document term matrix
predMatrix <- create_matrix(predictionData,originalMatrix=dtMatrix)
predMatrix
```
Notice that this time we provided the originalMatrix as a parameter. This is because we want the new matrix to use the same vocabulary as the training matrix.
Without this indication, the function will create a document term matrix using all the words of the test data (rainy, sunny, hello, this, is, another, world). It means that each sentence will be represented by a vector containing 7 values (one for each word) !

Such a matrix won't be compatible with the model we trained earlier because it expect vectors containing 2 values (one for rainy, one for sunny).

```{r}
# create the corresponding container
predSize = length(predictionData);
predictionContainer <- create_container(predMatrix, labels=rep(0,predSize), testSize=1:predSize, virgin=FALSE)
```

Two things are different:

we use a zero vector for labels, because we want to predict them
we specified testSize instead of trainingSize so that the data will be used for testing

```{r}
results <- classify_model(predictionContainer, model)
results

```

the probability is only  52% which means our model is not very confident on these two predictions.

sc: http://www.svm-tutorial.com/2014/11/svm-classify-text-r/
